Uncertainties in precipitation estimates from space-borne radar observations

### 2023-02-28 ucIrvine/presentation.tex
updates Feb 28

\documentclass{beamer}
\usepackage{graphicx}
\title{Uncertainties in precipitation
estimates from space-borne radar observations}
\author{Mircea Grecu}
\institute{NASA Goddard Space Flight Center and Morgan State University}
\date{March 2nd,2023}

@@

\end{document}

>>>>

\documentclass{beamer}
\usepackage{graphicx}
\title{Uncertainties in precipitation
estimates from space-borne radar observations}
\author{Mircea Grecu}
\institute{NASA Goddard Space Flight Center and Morgan State University}
\date{March 2,2023}
%%\date{\today}

@@

\frametitle{Ground Clutter}
    \item Ground clutter is strong echo in the radar observation caused 
    by the ground.
    \item It can extend up to 2.0 km above the surface and completely 
    obscure the precipitation echo.
    \item Nadir observations are minimally affected 
    and can be used in the development of statistical clutter mitigation 
    methodologies, e.g.
    $pRate(z<z_{cf})=pRate(z_{cf}) \times$
    $pRate_{mean}(z)/pRate_{mean}(z_{cf})$
        \includegraphics[width=0.9\textwidth]{Figures/fig9.png}
        \includegraphics[width=0.9\textwidth]{Figures/fig10.png}
\frametitle{Impact of Ground Clutter Correction}
        \includegraphics[width=0.9\textwidth]{Figures/fig11.png}
    \frametitle{Light Precipitation}
            \item The DPR does not miss all the light precipitation associated with a given point in the Tb-space
            \item An empirical algorithm may be derived from collocated Tbs and DPR retrievals
            \item The empirical algorithm is to be applied only when the DPR does not detect precipitation. When estimates are greater than 0, a decision is required.

            \end{itemize}
        \end{column}
        \begin{column}{0.5\textwidth}
            \begin{figure}
                \begin{center}
                \includegraphics[width=0.9\textwidth]{Figures/fig12.png}
                \includegraphics[width=0.9\textwidth]{Figures/fig13.png}
                \end{center}
            \end{figure}
        \end{column}
    \end{columns}
\end{frame} 
\begin{frame}
    \frametitle{Summary and Conclusions}
    \begin{itemize}
        \item Although the most accurate at the instantaneous level, space-borne radar precipitation 
        estimates affected by multiple types of uncertainties.
        \item Even when dual frequency observations are available, the 
        estimation problem is still posed.
        \item Parameterizations and "a priori" information derived 
        from ground observations may be used to mitigate the uncertainties.
        \item However, the process is not trivial and requires a sustained
        long-term effort.
    \end{itemize}
\end{frame}
\end{document}
